\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2019-12-01 the-proposal/the-proposal.tex
proposal: finally done the intro, maybe

\bibliographystyle{apsrev4-1}
\setlist{noitemsep}

@@

Because Vipassana is globally standardized, it affords researchers with definitive
solutions to the difficulties presented by varying teaching methodologies. In
exchange for this, the difficulty of long-term study is compounded by the intrinsic
seriousness demanded of a Vipassana practitioner: the concept of ``continuous
piercing awareness of constantly changing bodily sensation'' is not only a
requirement of serious Vipassana practice but could very well act as a surrogate
description of the practice itself. This seriousness poses obvious difficulties and
it is the intention of my study to begin breaking ground in solutions to those
difficulties.

@@

%\begin{thebibliography}{99}
%
%\bibitem{alteredtraits}
%  Goleman D., Davidson R.J.
%  \textit{Altered Traits.}
%  ISBN: 9780399184390. September 2018.
%
%\bibitem{davidson2015}
%  Davidson R.J., Kaszniak A.W.
%  \textit{Conceptual and methodological issues in research on mindfulness and meditation.}
%  American Psychologist, Volume 70(7), Pages 581-92. October 2015.
%  \url{https://doi.org/10.1037/a0039512}
%
%\bibitem{hildt2019}
%  Artificial Intelligence: Does Consciousness Matter?
%  \todo{stop doing this and use bibtex}
%
%\bibitem{entropicrevisited}
%  Carhart-Harris, Robin L.
%  \textit{The entropic brain - revisited}
%  NEUROPHARMACOLOGY, Vol: 142, Pages: 167-178, ISSN: 0028-3908, 2018.
%
%
%\end{thebibliography}
%
% \appendix*
% \input{sections/appendix1.tex}

>>>>

\setlist{noitemsep}

@@

Because Vipassana is globally standardized, it affords researchers with definitive
solutions to the difficulties presented by varying teaching methodologies. In
exchange for this, the difficulty of long-term study is compounded by the intrinsic
seriousness demanded of a Vipassana practitioner: the Pāli concept of \textit{ātāpī
  sampajāno satimā} (continuous piercing awareness of constantly
changing bodily sensation \cite{goenka1999discourses}) is not only a
requirement of serious Vipassana practice but could very well act as a surrogate
description of the practice itself. This seriousness poses obvious difficulties and
it is the intention of my study to begin breaking ground in solutions to those
difficulties.

@@

% \appendix*
% \input{sections/appendix1.tex}
